Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Finished editing section 7

In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge. Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques. For example,   two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately. The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more apples-to-apples comparison to observations of projected size. This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$

>>>>

In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge. Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques. For example,   two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately. The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more rigorous, ``apples-to-apples" comparison to observations of projected size. This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$
